Adapting the MVDR to a GPU for active sonar systems of different sizes.

### 2013-01-20 ASA2013/asa2013.tex
la2pdf commit - 2013:01:20	15:35:38	(sø.20.jan.)

\begin{abstract}
The MVDR beamformer has been shown to improve active sonar image quality compared to conventional methods. Unfortunately, it is also significantly more computationally expensive because a spatial covariance matrix must be estimated and inverted for each image pixel. We target this challenge by altering and mapping MVDR to a GPU, and suggest three different solutions depending on the system size.

For systems with relatively few channels, we suggest arithmetic optimizations for the estimation step, and show how a GPU can be used to yield image creation rates of more than 1\,Mpx/s. For larger systems we show that frequency domain processing is preferable. This promotes high processing rates at a negligible reduction in image quality. These GPU implementations consistently reduced the runtime by 2-3 orders of magnitude compared to our reference C and Matlab implementations.

@@

\ \\
Total: 192 words (200 max)

>>>>

\begin{abstract}
The MVDR beamformer has been shown to improve active sonar image quality compared to conventional methods. Unfortunately, it is also significantly more computationally expensive because a spatial covariance matrix must be estimated and inverted for each image pixel. We target this challenge by altering and mapping the MVDR beamformer to a GPU, and suggest three different solutions depending on the system size.

For systems with relatively few channels, we suggest arithmetic optimizations for the estimation step, and show how a GPU can be used to yield image creation rates of more than 1\,Mpx/s. For larger systems we show that frequency domain processing is preferable, as this promotes high processing rates at a negligible reduction in image quality. These GPU implementations consistently reduced the runtime by 2-3 orders of magnitude compared to our reference C and Matlab implementations.

@@

\ \\
Total: 195 words (200 max)
